Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-20 paper/app-pineappl.tex
Revise appendix

\lstset{
  basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}

@@

The command-line program \texttt{pineappl} is compiled and installed using
\begin{lstlisting}[language=bash]
cargo install pineappl_cli
\end{lstlisting}
This program also needs \texttt{LHAPDF} installed.
For usage instructions simply type \texttt{pineappl} in your shell and read the help message.

For the C interface you need to first install \texttt{cargo-c}, download the \textsc{PineAPPL} repository, and compile and finally install into it into a directory \texttt{\$prefix} as follows:
\begin{lstlisting}[language=bash]
cargo install cargo-c
git clone https://github.com/N3PDF/pineappl/
cd pineappl_capi/
cargo cinstall --release --prefix=${prefix}
\end{lstlisting}
The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}).
Make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
The latter is needed for \texttt{pkg-config -{}-cflags -{}-libs pineappl\_capi} to work, which prints the necessary compiler/linker flags.
See App.~\ref{app:example-program} for an example.

@@

The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
The full example can be found at TODO.
\begin{lstlisting}[language=C++,mathescape=true]
// create a new luminosity function for the $\gamma\gamma$ initial state
auto* lumi = pineappl_lumi_new();
int32_t pdg_ids[] = { 22, 22 };
double ckm_factors[] = { 1.0 };
pineappl_lumi_add(lumi, 2, pdg_ids, ckm_factors);

@@

// destroy the object
pineappl_grid_delete(grid);
\end{lstlisting}

>>>>

\subsubsection*{Installation of Rust}

\lstset{
  basicstyle=\ttfamily\small,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}

@@

\subsubsection*{Installation of the command-line program \texorpdfstring{\texttt{pineappl}}{pineappl}}

The command-line program \texttt{pineappl} is compiled and installed using
\begin{lstlisting}[language=bash]
cargo install pineappl_cli
\end{lstlisting}
This program also needs \texttt{LHAPDF} \cite{Buckley:2014ana} installed.
For usage instructions simply type \texttt{pineappl} in your shell and read the help message.

\subsubsection*{Installation of the C-language interface (optional)}

For the C interface you need to first install \texttt{cargo-c},
\begin{lstlisting}[language=bash]
cargo install cargo-c
\end{lstlisting}
and then download the \textsc{PineAPPL} repository, compile and finally install into it into a directory \texttt{\$prefix} as follows:
\begin{lstlisting}[language=bash]
git clone https://github.com/N3PDF/pineappl/
cd pineappl_capi/
cargo cinstall --release --prefix=${prefix}
\end{lstlisting}
The last line will install the C header \texttt{pineappl\_capi.h}, the library, and a pkg-config\footnote{A standard way on Linux to express how dependencies are compiled/linked against, see \url{https://www.freedesktop.org/wiki/Software/pkg-config/}} file (\texttt{pineappl\_capi.pc}).
Make sure that the environment variables \texttt{PATH}, \texttt{LD\_LIBRARY\_PATH}, and \texttt{PKG\_CONFIG\_PATH} are properly set.
The latter is needed for \texttt{pkg-config -{}-cflags -{}-libs pineappl\_capi} to work, which prints the necessary compiler/linker flags.
See App.~\ref{app:example-program} for an example.

@@

The following listing shows how to setup \textsc{PineAPPL} using its C interface in a simple Monte Carlo integrator for calculating the double-photon contribution to Drell--Yan lepton-pair production at the LHC.
All \textsc{PineAPPL} functions have the prefix \texttt{pineappl\_}.
The full example can be found at \url{https://github.com/N3PDF/pineappl/tree/master/examples/capi-dy-aa}.

\clearpage
\begin{lstlisting}[language=C++,mathescape=true]
// create a new luminosity function for the $\gamma\gamma$ initial state
auto* lumi = pineappl_lumi_new();
int32_t pdg_ids[] = { 22, 22 };
double ckm_factors[] = { 1.0 };
pineappl_lumi_add(lumi, 1, pdg_ids, ckm_factors);

@@

// destroy the object
pineappl_grid_delete(grid);
\end{lstlisting}
\clearpage
